Plots_Genome

### 2024-04-04 Code/Plots_Genome.Rmd
Corrected missing y axis

@@

         axis.title.y = element_blank(),

@@

```{r, ProchlorococcusEnzymeKms ggsave, include = FALSE} 
ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms.png"), plot = ProchlorococcusEnzymeKms, height = 20, width = 17)
ggsave(filename = file.path(PLOSFiguresRoundX, "Fig11.tiff"), plot = ProchlorococcusEnzymeKms, height = 20, width = 17, compression = "lzw")
```

>>>>

         # Strain %in% c("CCMP1986", "MIT9313"),

@@

         # axis.title.y = element_blank(),

@@

```{r, ProchlorococcusEnzymeKms ggsave, include = FALSE} 
ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms.png"), plot = ProchlorococcusEnzymeKms, height = 23, width = 17)
ggsave(filename = file.path(PLOSFiguresRoundX, "Fig11.tiff"), plot = ProchlorococcusEnzymeKms, height = 20, width = 17, compression = "lzw")
# ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms_julie.png"), plot = ProchlorococcusEnzymeKms, height = 23, width = 17)
```
